Viscous Transport in Eroding Porous Media

### 2019-08-05 docs/transport/erosion_transport.tex
modify figures of transport paper

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.51\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
nearly touching eroding bodies versus normalized time. (b): The incoming
flow rate, $U$, for a fixed pressure drop across the channel versus
normalized time.  The flow rate is initially very small, but it
eventually increases as a power law (dashed line) towards the flow rate
$U=1$ that occurs once all the bodies have eroded.}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.45\textwidth}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
\todo[inline]{S-H: Can cut the ylimit at 1.3}
\caption{}
\end{subfigure}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_diff_top10_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of an eroded geometry
with porosity 62.9\%. (a) The x-component of the velocity $u(-1, y)$
normalized by its maximum velocity of $2.98 \times 10^{-3}$. (b) The
local tortuosity $\tau(y)$ on the cross section $x = -1$.  The spatially
averaged tortuosity through the channel is $1.098$.  (c) The
trajectories resulting in the ten largest differences between
neighboring trajectories.  Neighboring trajectories have the same
color.}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian approach of tortuosity. 
The blue dots are Eulerian approach of tortuosity and the red stars and 
square are Lagrangian approach of tortuosity.}
\end{figure}

>>>>

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
nearly touching eroding bodies versus normalized time. (b): The incoming
flow rate, $U$, for a fixed pressure drop across the channel versus
normalized time.  The flow rate is initially very small, but it
eventually increases as a power law (dashed line) towards the flow rate
$U=1$ that occurs once all the bodies have eroded.}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.45\textwidth}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =0.97\linewidth]{./figs/tort_local20_268}
\todo[inline]{S-H: Can cut the ylimit at 1.3}
\caption{}
\end{subfigure}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_diff_top10_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of an eroded geometry
with porosity 62.9\%. (a) The x-component of the velocity $u(-1, y)$
normalized by its maximum velocity of $2.98 \times 10^{-3}$. (b) The
local tortuosity $\tau(y)$ on the cross section $x = -1$.  The spatially
averaged tortuosity through the channel is $1.098$.  (c) The
trajectories resulting in the ten largest differences between
neighboring trajectories.  Neighboring trajectories have the same
color.}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian approach of tortuosity. 
The blue dots are Eulerian approach of tortuosity and the red stars and 
square are Lagrangian approach of tortuosity. 
The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and 
the the sum $S$ of squared residuals is 0.0075.}
\end{figure}
